Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-13 ms.tex
outlined softmax supplement

\begin{figure}
  \caption{Comparison of expected payoffs from our computational anaysis (solid
    lines with circles), expected individual payoffs with no social learning
    (dashes without markers), and expected payoffs for all-social learner 
    populations. Only four plots shown to enhance detail; see supplement for
    five additional plots.
clarity.} 
  \label{fig:payoffs}
\centering
    \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
\end{figure}

@@

>>>>

\begin{figure}
  \caption{Comparison of expected payoffs from our computational anaysis (solid
    lines with circles), expected individual payoffs with no social learning
    (dashes without markers), and expected payoffs for all-social learner 
    populations. Only four plots shown to enhance detail; see supplement for
    five additional plots.
} 
  \label{fig:payoffs}
\centering
    \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
\end{figure}

@@

\begin{itemize}
  \item 
    We tested two additional settings of the softmax behavior selection
    greediness parameter, $\beta=0.01,1.0$, which reproduced qualitative patterns in
    the evolution of social learning. 
  \item
    We see that certain details are changed within this broad agreement between
    results obtained with different $\beta$. 
    \begin{enumerate}
      \item 
        More drift when $\beta=1$, which can be seen in certain $(\pilow, B)$ pairs
        (entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}b). 
        For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
        data points with greater drift, i.e., where $\meansl \approx 0.5$. 
    \end{enumerate}
\end{itemize}
